---
title: "Eating Out"
author: "Syslee Evans"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Methods

response variable is catagorical: dine out last week? yes or no 

explanitory variale is race, it, too, is a catagorical variable.
so we use cat~cat

inference: chi_squared and fisher exact tests 

# Discriptive summaries 

## Graphical summary

### barchart

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

Based on our barchart you can clearly see that the white people eatout more than black and other race. Black and other race eat out about the same amount.




